---
title: "ggplot_exercises"
author: "Jordan McNea"
date: "11/11/2020"
output: html_document
---
## This script gives us some practice on ggplot

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(scales)
library(RColorBrewer)
```

## Switch working directory so we can read locally

```{r Read in data}
setwd('C:/Users/Jordan/Dropbox/GA Work/John Chandler/ggplot_exercise_data/')

gd <- read_tsv("grocery_data.txt")
month.summary <- read_tsv("month_summary.txt")
dept.summary <- read_tsv("dept_summary.txt")
mosaic.data <- read_tsv("counts_for_mosaic.txt")

```

## Problem 1 - dotchart of sales by month by department
### Things to add:
* Divide sales by 1000
* Add some transparency to the points with `alpha`
* Add axis labels and a title using `labs`
* Center the title, rather than it being left-aligned

```{r prob 1}
gd <- gd %>%
    mutate(month = as.factor(month),
           departmentName = reorder(departmentName,ownerSales,mean))
head(gd,10)

# Here's a basic one:
ggplot(gd, aes(x=ownerSales,y=departmentName)) + 
  geom_point() 

```

## Problem 2 - add median lines
### add these lines to the plot using geom_segment.
* That function/layer takes four values
* x, xend, y, and y.end. You can get y.values with
* something like "as.numeric(departmentName)-0.5" (or plus)
* The x's should be the median values


```{r median lines}

medians <- gd %>% 
  group_by(departmentName) %>%
  summarise(med.val = median(ownerSales/1000))

medians

ggplot(gd, aes(x=ownerSales/1000,y=departmentName)) + 
  geom_point()


```

## Problem 3 - line chart plotting the density
### Things to add:
* a theme (could use theme_minimal)
* label each line using geom_text
* Make sure labels don't overlap the line (use check_overlap=T within geom_text to accomplish this)
* Each label should match the color of the line its labeling

```{r prob 3}

p3.size <- 4
p3.cols <- c("gray15","gray40","gray75")
p <- ggplot(gd,
            aes(x=ownerSales/1000)) + 
  ylab("Density") + 
  geom_line(stat="density",col=p3.cols[1],size=1.25,bw=1) + 
  geom_line(stat="density",col=p3.cols[2],size=1.25,bw=5) + 
  geom_line(stat="density",col=p3.cols[3],size=1.25,bw=25) + 
  scale_x_continuous(label=dollar) + 
  xlab("Monthly Sales (000)") + 
  geom_text(aes(x=20,y=0.05),
            label= 'Bandwidth = 1', 
            size=p3.size) + 
  geom_text(aes(x=20.5,y=0.03),
            label= 'Bandwidth = 5',
            size=p3.size) + 
  geom_text(aes(x=75,y=0.009), 
            label='Bandwidth = 25',
            size=p3.size)

p

```

## Problem 4 - use `gd` to create a density plot of sales by department. 
### Things to add:
* First, make a density plot of sales (using geom_density). 
* Then facet that plot by department using `facet_wrap` (There should a density plot for each department)
* Change the x axis tickmarks so they are easily readable

```{r prob 4}

ggplot(gd, aes(ownerSales, ..count..)) +
  geom_density(adjust = 5)

```

## Problem 5 - violin plots! Use gd, build violin plots of ownerSales by department. 
### Things to add: 
* add quantile lines, use nice labels,
* re-orient chart with departments on the y-axis 
* add a vertical line for the overall mean and change its color
* add an annotation to the mean line with the mean sales


```{r prob 5}

ggplot(gd, aes(departmentName,ownerSales)) +
  geom_violin(scale='width',trim=FALSE)


```


## Problem 6 - Mosaic charts
### Things to add:
* Using mosaic.table, create a mosaic plot


```{r prob 6}

mosaic.table <- mosaic.data %>% 
  spread(Segment,count) %>% 
  rename(Dept=DepartmentName) %>% 
  arrange(Primary) %>% 
  as.data.frame
  
head(mosaic.table,10)
# Let's do some renaming
row.names(mosaic.table) <- mosaic.table$Dept
mosaic.table$Dept <- NULL

rownames(mosaic.table)[rownames(mosaic.table)=="SUPPLEMENTS"] <- "SUPP."
rownames(mosaic.table)[rownames(mosaic.table)=="REF GROCERY"] <- "REF GROC"
rownames(mosaic.table)[rownames(mosaic.table)=="PACKAGED GROCERY"] <- "PKG GROC"


```

